Quality Metrics for SKOS Vocabularies

### 2012-03-13 introduction.tex
added stw example version info

	\item \todo{CM}{An earlier version of the STW thesaurus contained 5 pairs of concepts with identical labels}. As a result, the auto-complete function of the online search interface suggested identical entries, without giving disambiguation information.

>>>>

	\item \todo{CM}{An earlier version, the STW thesaurus (8.06) contained 5 pairs of concepts with identical labels}. As a result, the auto-complete function of the online search interface at that time suggested identical entries, without giving disambiguation information.
